Staged Abstract Interpreters

### 2019-09-11 paper/80_related.tex
0-cfa
misc

\paragraph{Control-flow Analysis} Our case studies and evaluation focus on
control-flow analysis for functional languages
\cite{Shivers:1991:SSC:115865.115884, Midtgaard:2012:CAF:2187671.2187672}. In
general, $k$-CFA (where $k > 0$) is considered impractical to be used as a
compiler pass, due to its EXPTIME lower bound
\cite{VanHorn:2008:DKC:1411204.1411243}.  However, several variants of 0CFA
were developed and shown to be useful in practice
\cite{Adams:2011:FTR:2048066.2048105, Bergstrom:2014:PEH:2628136.2628153,
ashley:practical, Reppy:2006:TCA:1159876.1159888}.

\paragraph{Two-level Semantics} The idea of reinterpreting the semantics as
abstract interpretation can be traced to Nielson's two-level semantics
\cite{NIELSON1989117}; using two-level semantics for code generation
was also explored by \citet{NIELSON198859}.
\citet{Sergey:2013:MAI:2491956.2491979}'s monadic abstract
interpreter is closely related to the two-level semantics: the
use of a generic interface with monads and then reinterpreting it with
different semantics is already two-level. Instead of focusing on
semantics, this paper shows how a staged analyzer can be built and
used to increase efficiency of static analyses. We augment the monadic
abstract interpreter with binding-time polymorphism, using code generation to
produce efficient low-level code. The presented work can be considered as
a two-dimensional application of the two-level semantics.

>>>>

\paragraph{Control-flow Analysis} Our case studies and evaluation focus on
control-flow analysis for functional languages
\cite{Shivers:1991:SSC:115865.115884, Midtgaard:2012:CAF:2187671.2187672}. In
general, $k$-CFA (where $k > 0$) is considered impractical to be used as a
compiler pass, due to its EXPTIME lower bound
\cite{VanHorn:2008:DKC:1411204.1411243}.  However, several variants of 0-CFA
were developed and shown to be useful in practice
\cite{Adams:2011:FTR:2048066.2048105, Bergstrom:2014:PEH:2628136.2628153,
ashley:practical, Reppy:2006:TCA:1159876.1159888}.

\paragraph{Two-level Semantics} The idea of reinterpreting the semantics as
abstract interpretation can be traced to Nielson's two-level semantics
\cite{NIELSON1989117}. Using two-level semantics for code generation
was also explored by \citet{NIELSON198859}.
\citet{Sergey:2013:MAI:2491956.2491979}'s monadic abstract
interpreter is closely related to the two-level semantics: the
use of a generic interface with monads and then reinterpreting it with
different semantics is already two-level. Instead of focusing on
semantics, this paper shows how a staged analyzer can be built and
used to increase efficiency of static analyses. We augment the monadic
abstract interpreter with binding-time polymorphism, using code generation to
produce efficient low-level code. The presented work can be considered as
a two-dimensional application of the two-level semantics.
